Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Workshop Using Cutting-Edge Tools

### 2021-01-09 paper_contents.tex
Update @seo2019 bib entry

The second relevant theoretical idea is accessibility. Accessibility refers to 
the state of digital technologies, including web-based materials, not having barriers
to their use. Accessibility is particularly relevant to sharing scholarly work [@seo2019];
a number of tools have made writing not only text but also code including the typesetting 
language LaTeX and R Markdown,  the latter of which can allow for written text and analytic 
R code to be woven together in a way that can make code more easy to understand [@knuth1984].

>>>>

The second relevant theoretical idea is accessibility. Accessibility refers to 
the state of digital technologies, including web-based materials, not having barriers
to their use. Accessibility is particularly relevant to sharing scholarly work [seo2019arow];
a number of tools have made writing not only text but also code including the typesetting 
language LaTeX and R Markdown,  the latter of which can allow for written text and analytic 
R code to be woven together in a way that can make code more easy to understand [@knuth1984].
